---
title: "W6 Assignment"
output: html_notebook
---
1. Define a defensive function that calculates the Gross Domestic Product of a nation from the data available in the gapminder dataset. Using that function, calculate the GDP of Denmark in the following years: 1967, 1977, 1987, 1997, 2007, and 2017.

```{r}
library(gapminder)
library(tidyverse)
```

```{r}
calcGDP <- function(selected_year = NULL, selected_country = NULL) {
	# Make sure we do not exit out of our script just because of a silly missing record:
	tryCatch({
		# Make sure the year is in the dataset and that country is a string:
		stopifnot(selected_year %in% gapminder$year | is.character(selected_country))
	
		gdp_df <- gapminder %>%
			filter(country == selected_country & year == selected_year)
	
		# Make sure we are only getting one record:
		stopifnot(nrow(gdp_df) == 1)
	
		return(gdp_df$pop * gdp_df$gdpPercap)
	},
	error = function(msg) {
		print(msg)
		return(NA)
	})
}

# Check all of the years:
for (year in c(1967, 1977, 1987, 1997, 2007, 2017)) {
	print(str_c(year, ': ', round(calcGDP(year, 'Denmark'))))
}
```
As expected, we get an error on 2017, since the year is not present in the records. We can verify this by looking at the years present in the gapminder dataset:
```{r}
2017 %in% distinct(gapminder, year)
```
2. Write a script that loops over each country in the gapminder dataset, tests whether the country starts with a ‘B’ , and print out whether the life expectancy is smaller than 50, between 50 and 70, or greater than 70.
```{r}
# We we loop through all indices of gapminder's rows:
for (index in 1:nrow(gapminder)) {
	# And select the actual row with the given index:
	gapminder_record <- gapminder[index,]
   
	# Isolate the row's values of the given columns:
  country <- as.character(gapminder_record[['country']])
  lifeExp <- gapminder_record[['lifeExp']]
  year <- gapminder_record[['year']]
  
  # We don't want to repeat ourselves too much:
  base_message <- paste('The life expectancy of', country, 'in the year', year, 'is')
  
  
  if ((startsWith(country, 'B'))) {
  	if (lifeExp < 50) {
    	print(paste(base_message, 'less than 50 years'))
  		
    } else if (lifeExp <= 70) {
    	print(paste(base_message, 'between 50 and 70 years'))
   
    } else {
    	print(paste(base_message, 'more than 70 years'))
    }
  }
}
```




